### 2025-07-17 paper/quarto_aaai/paper.tex
not sure what the hell quarto is doing now
bloody hell

Today's prominence of artificial intelligence (AI) has largely been
driven by the success of representation learning with large degrees of
freedom: instead of relying on features and rules hand-crafted by
humans, modern machine learning (ML) models are tasked with learning
highly complex representations directly from the data, guided by narrow
objectives such as predictive accuracy \citep{goodfellow2016deep}. These
models tend to be so complex and opaque that humans cannot easily
interpret their decision-making.

@@

@@

\begin{table*}

\caption{\label{tbl-main}Key performance metrics and bootstrapped
standard errors (omitted if essentially zero) for all datasets.
\textbf{Plausibility} (columns 1-2): percentage reduction in
implausibility for \(\text{IP}\) and \(\text{IP}^*\), respectively;
\textbf{Actionability} (column 3): percentage reduction in costs with
protected features. \textbf{Accuracy} (columns 4-7): test accuracies and
robust accuracies (\(\text{Acc}^*\)) for CT and the baseline (BL).
Counterfactual outcomes (col.~1-3) are aggregated across bootstrap
samples and varying degrees of the energy penalty
\(\lambda_{\text{egy}}\) used for \emph{ECCo} at test time. Asterisks
(\(^*\)) in columns 1-3 indicate that bootstrapped 99\%-confidence
interval of differences in mean outcomes does \emph{not} include zero.
Standard errors for accuracy (col.~4-7) are bootstrapped from the test
set.}

@@

@@

\end{table*}%

>>>>

Today's prominence of artificial intelligence (AI) has largely been
driven by the success of representation learning with large degrees of
freedom: instead of relying on features and rules hand-crafted by
humans, modern machine learning (ML) models are tasked with learning
highly complex representations directly from the data, guided by narrow
objectives such as predictive accuracy \citep{goodfellow2016deep}. These
models tend to be so complex that humans cannot easily interpret their
decision-making.

@@

\begin{table}

\caption{\label{tbl-main}Key counterfactual evaluation metrics and
bootstrapped standard errors for all datasets. \textbf{Plausibility}
(columns 1-2): percentage reduction in implausibility for \(\text{IP}\)
and \(\text{IP}^*\), respectively; \textbf{Actionability} (column 3):
percentage reduction in costs with protected features. Outcomes are
aggregated across bootstrap samples and varying degrees of the energy
penalty \(\lambda_{\text{egy}}\) used for \emph{ECCo} at test time.
Asterisks (\(^*\)) indicate that bootstrapped 99\%-confidence interval
of differences in mean outcomes does \emph{not} include zero.}

\end{table}%

@@

@@

\pandocbounded{\includegraphics[keepaspectratio]{../../paper/figures/acc.png}}

@@

\caption{\label{fig-acc}Test accuracies on adversarially perturbed data
with varying perturbation sizes for all non-synthetic datasets.}

### 2025-07-17 paper/sections/experiments.qmd
bloody hell

![Test accuracies on adversarially perturbed data with varying perturbation sizes for all non-synthetic datasets.](paper/figures/acc.png){#fig-acc fig-env="figure*"}

>>>>

![Test accuracies on adversarially perturbed data with varying perturbation sizes for all non-synthetic datasets.](/paper/figures/acc.png){#fig-acc fig-env="figure*"}
